Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-24 main_paper.tex
[#13] strengthen equivalence claims between CCT's correction and ours
The proof of Theorem 1 indicates that the bootstrap bias correction
is equivalent to CCT's correction, after abstracting from bootstrap
simulation error. This commit makes that equivalence explicit and
addresses part of Referee 1's first two comments.

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}.}}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2}.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$
    with least squares using $K_{-,b}$ and $K_{+,b}$ for weights:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
    \end{align*}
    Let
    \[
      \hat g(x) = \begin{cases}
        \hat g_-(x) & \textif\ x < 0 \\
        \hat g_+(x) & \otherwise
      \end{cases}
    \]
    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$ for all $i$.
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th replication:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
      \end{align*}
      for all $i$.
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$ for
      weights:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i =1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{-,h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{+,h}(X_{i}).
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9} and
$V^{bc}(h, b) = V(h) + C(h, b)$, both which are defined in Equations~\eqref{eq:8}
and~\eqref{eq:13} of the Mathematical Appendix.
\end{theorem}

Theorem~\ref{T1} implies that our bias-corrected
estimator has the same asymptotic distribution as CCT's. This equivalence should
be unsurprising; both estimators use a second order polynomial to directly estimate
the bias of the local linear model, so they should behave very similarly.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for
the analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else and assume, with some abuse of notation, that the
dimension of $e_p$ adapts to make matrix and vector operations
conformable. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{equation*}
  Y_i^* =
  \begin{cases}
    r_2(X_i/b)'H_2(b)^{-1} \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
    r_2(X_i/b)'H_2(b)^{-1} \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
  \end{cases}
\end{equation*}
which, along with the definitions at the beginning of the appendix,
ensures that
\begin{align*}
  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

@@

Normality also follows standard arguments for the wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$p$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
\rvert^{p}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i) +
  (h/b)^2 \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish
that
\begin{equation}\label{eq:17}
  \tfrac{1}{n} \sum_{i} m^{1+\delta} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta}.
\end{equation}
obeys the LLN, implying that~\eqref{eq:17} holds and completing the proof. \qed

>>>>

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, Third Annual Conference of the International Association for Applied Econometrics,
 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
  substantial help and advice on earlier versions of this paper.}}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2}.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$
    with least squares using $K_{-,b}$ and $K_{+,b}$ for weights:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      (\hat\beta_{-,0}, \hat\beta_{-,1}, \hat\beta_{-,2})' &=
      \argmin_{\beta_0, \beta_1, \beta_2}
      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
      (\hat\beta_{+,0}, \hat\beta_{+,1}, \hat\beta_{+,2})' &= \argmin_{\beta_0, \beta_1, \beta_2}
      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
    \end{align*}
    Let
    \[
      \hat g(x) = \begin{cases}
        \hat g_-(x) & \textif\ x < 0 \\
        \hat g_+(x) & \otherwise
      \end{cases}
    \]
    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$ for all $i$.
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th replication:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
      \end{align*}
      for all $i$.
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$ for
      weights:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i =1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{-,h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{+,h}(X_{i}).
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:18}
  \Delta^*(h,b) = h^{2} \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{equation}
almost surely and
\begin{equation}
  \label{eq:4}
  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9} and
$V^{bc}(h, b) = V(h) + C(h, b)$, both which are defined in Equations~\eqref{eq:8}
and~\eqref{eq:13} of the Mathematical Appendix.
\end{theorem}

For practical purposes, Theorem~\ref{T1} implies that our bias-corrected
estimator has the same asymptotic distribution as CCT's. This equivalence should
be unsurprising; both estimators use a second order polynomial to directly estimate
the bias of the local linear model, so they should behave very similarly.
Equation~\eqref{eq:18} implies an even stronger relationship between the two
results, that the bias correction is equivalent to CCT's up to simulation error
in the bootstrap.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for
the analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE.
As we remark earlier, the bias correction from the wild bootstrap is equivalent
to CCT's bias correction up to simulation error from the bootstrap and this
equivalence is apparent in the Monte Carlo. This equivalence also explains why
the bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.\footnote{%
  Note that this table reports the estimators' variance across simulations,
  not the \emph{estimated} variance used for the confidence intervals.} %

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else and assume, with some abuse of notation, that the
dimension of $e_p$ adapts to make matrix and vector operations
conformable. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du.
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1). \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{equation*}
  Y_i^* =
  \begin{cases}
    r_2(X_i/b)'H_2(b)^{-1} \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
    r_2(X_i/b)'H_2(b)^{-1} \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
  \end{cases}
\end{equation*}
which, along with the definitions at the beginning of the appendix,
ensures that
\begin{align*}
  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
Equation~\eqref{eq:18} holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely.

CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

@@

Normality also follows standard arguments for the wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$q$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^q \E \lvert e_i^*
\rvert^{q}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i) +
  (h/b)^2 \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish
that
\begin{equation}\label{eq:17}
  \tfrac{1}{n} \sum_{i} m^{1+\delta} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta}.
\end{equation}
obeys the LLN, implying that~\eqref{eq:17} holds and completing the proof. \qed
